Motional Ground State Cooling Outside the Lamb-Dicke Regime

### 2017-08-15 paper.tex
Cover letter
Move figures for PRL submission

\begin{figure}[b]
  \includegraphics[width=8.5cm]{imgs/fig2_raman_op.pdf}
  \caption{Optical pumping motional-state redistribution and Raman coupling for large LD parameters for the axial direction ($z$). The range plotted covers $95$\% of the initial thermal distribution.
    (A) Motional state distribution after one OP cycle for different initial states motion,
    $n_{\textrm{init}}$. Due to photon-recoil and the large LD parameter, $\eta^{\textrm{OP}}_z=0.6$,
    there is a high probability of $n$ changing.
    (B) Matrix elements for Raman transition deviate from
    $\sqrt{n}$ scaling with multiple minima. During cooling, we utilize the fact that high motional states couple most effectively to sidebands with large $|\Delta n|$.
    \label{f-ld}}
\end{figure}

@@

\begin{figure*}
  \includegraphics[height=4.2cm]{imgs/spectrum_r.pdf}
  \includegraphics[height=4.2cm]{imgs/rabi_flop_r3_0.pdf}
  \includegraphics[height=4.2cm]{imgs/rabi_flop_r3_p1.pdf}
  \caption{(A) Left to right: Radial Raman sideband spectrum of $\Delta n_y=1,\,\Delta n_x=1,\,\Delta n_x=-1,\,\Delta n_y=-1,\,\Delta n_x=-2,\,\Delta n_y=-2$ before and after Raman sideband cooling.
    (B,C) Rabi flopping on axis $y$ (B) carrier and (C) $\Delta n_y=1$ sideband
    before (red circle) and after (blue square) RSC.
    Solid lines in (B) and (C) are fits to a Rabi-flopping
    that includes a thermal distribution of motional states~\cite{Meekhof1996}
    as well as off-resonant scattering from the Raman beams.
    The curves reach a maximum contrast of 85\% (horizontal dashed line)
    because 5\% of atoms are lost from one imaging step to the next,
    and 10\% of atoms are additionally lost during Raman cooling.
    The blue lines correspond to a 1D ground state probability of $93$\%
    after cooling (not including loss) and
    the red lines correspond to a thermal distribution of $70$ $\mu$K before RSC.
    \label{f-radial}}
\end{figure*}
\begin{figure*}
  \includegraphics[height=4.2cm]{imgs/spectrum_a1.pdf}
  \includegraphics[height=4.2cm]{imgs/rabi_flop_a1_0.pdf}
  \includegraphics[height=4.2cm]{imgs/rabi_flop_a1_p1.pdf}
  \caption{(A) Left to right: Axial Raman sideband spectrum from $\Delta n_z=1,0,-1,\ldots,-8$
    before and after Raman sideband cooling.
    (B,C) Rabi flopping on axial (B) carrier $\Delta n_z=0$  and (C) $\Delta n_z=1$ sideband
    before (red circle) and after (blue square) RSC.
    Solid blue lines in (B) and (C), similar to Fig.~\ref{f-radial}B and C,
    are fits to the Rabi flopping and yield a ground state probability of $92$\%
    after cooling (not including the 15\% population loss) and
    the red lines correspond to a thermal distribution of $70$ $\mu$K before RSC.
    The green line in (C), includes the additional decoherence due to
    a fluctuation of the hyperfine splitting of magnitude $3$ kHz.
    We see that the decoherence effect is strongest for the post-cooling data on
    the $\Delta n_z=1$ sideband where the Rabi frequency is the lowest.
    The horizontal dashed line shows the overall survival after cooling and imaging.
    \label{f-axial}}
\end{figure*}

>>>>

\begin{figure}[b]
  \includegraphics[width=8.5cm]{fig2_raman_op.pdf}
  \caption{Optical pumping motional-state redistribution and Raman coupling for large LD parameters for the axial direction ($z$). The range plotted covers $95$\% of the initial thermal distribution.
    (A) Motional state distribution after one OP cycle for different initial states motion,
    $n_{\textrm{init}}$. Due to photon-recoil and the large LD parameter, $\eta^{\textrm{OP}}_z=0.6$,
    there is a high probability of $n$ changing.
    (B) Matrix elements for Raman transition deviate from
    $\sqrt{n}$ scaling with multiple minima. During cooling, we utilize the fact that high motional states couple most effectively to sidebands with large $|\Delta n|$.
    \label{f-ld}}
\end{figure}

@@

\begin{figure*}
  \includegraphics[height=4.2cm]{spectrum_r.pdf}
  \includegraphics[height=4.2cm]{rabi_flop_r3_0.pdf}
  \includegraphics[height=4.2cm]{rabi_flop_r3_p1.pdf}
  \caption{(A) Left to right: Radial Raman sideband spectrum of $\Delta n_y=1,\,\Delta n_x=1,\,\Delta n_x=-1,\,\Delta n_y=-1,\,\Delta n_x=-2,\,\Delta n_y=-2$ before and after Raman sideband cooling.
    (B,C) Rabi flopping on axis $y$ (B) carrier and (C) $\Delta n_y=1$ sideband
    before (red circle) and after (blue square) RSC.
    Solid lines in (B) and (C) are fits to a Rabi-flopping
    that includes a thermal distribution of motional states~\cite{Meekhof1996}
    as well as off-resonant scattering from the Raman beams.
    The curves reach a maximum contrast of 85\% (horizontal dashed line)
    because 5\% of atoms are lost from one imaging step to the next,
    and 10\% of atoms are additionally lost during Raman cooling.
    The blue lines correspond to a 1D ground state probability of $93$\%
    after cooling (not including loss) and
    the red lines correspond to a thermal distribution of $70$ $\mu$K before RSC.
    \label{f-radial}}
\end{figure*}
\begin{figure*}
  \includegraphics[height=4.2cm]{spectrum_a1.pdf}
  \includegraphics[height=4.2cm]{rabi_flop_a1_0.pdf}
  \includegraphics[height=4.2cm]{rabi_flop_a1_p1.pdf}
  \caption{(A) Left to right: Axial Raman sideband spectrum from $\Delta n_z=1,0,-1,\ldots,-8$
    before and after Raman sideband cooling.
    (B,C) Rabi flopping on axial (B) carrier $\Delta n_z=0$  and (C) $\Delta n_z=1$ sideband
    before (red circle) and after (blue square) RSC.
    Solid blue lines in (B) and (C), similar to Fig.~\ref{f-radial}B and C,
    are fits to the Rabi flopping and yield a ground state probability of $92$\%
    after cooling (not including the 15\% population loss) and
    the red lines correspond to a thermal distribution of $70$ $\mu$K before RSC.
    The green line in (C), includes the additional decoherence due to
    a fluctuation of the hyperfine splitting of magnitude $3$ kHz.
    We see that the decoherence effect is strongest for the post-cooling data on
    the $\Delta n_z=1$ sideband where the Rabi frequency is the lowest.
    The horizontal dashed line shows the overall survival after cooling and imaging.
    \label{f-axial}}
\end{figure*}
